### 2010-04-01 papers/icfp-2010-desc/paper_discussion.tex
Desc@ICFP: update TODO list.

We share with Generic Haskell the \emph{type-indexed data type}
approach~\cite{hinze:generic-haskell}, as exemplified by the free
monad construction: from datatype, we can compute new datatypes and
equip them with their structure. Generic Haskell also features
\emph{generic views}~\cite{holdermans:generic-view}, transparently
transforming the structure of datatype definitions. An example is the
tagged descriptions, presenting datatypes under a sum-of-sigmas
angle. Unlike Generic Haskell, we do not have to modify the compiler
to obtain views on datatypes: we can massage descriptions from inside
our language.

>>>>

We share with Generic Haskell the \emph{type-indexed datatype}
approach~\cite{hinze:generic-haskell}, as exemplified by the free
monad construction: from datatype, we can compute new datatypes and
equip them with their structure. Generic Haskell also features
\emph{generic views}~\cite{holdermans:generic-view}, transparently
transforming the structure of datatype definitions. An example is the
tagged descriptions, presenting datatypes under a sum-of-sigmas
angle. Unlike Generic Haskell, we do not have to modify the compiler
to obtain views on datatypes: we can massage descriptions from inside
our language.
